Compositional Certified Resource Bounds\ifshort{\vspace{-.15cm}}{}

### 2014-11-05 paper/main.tex
add the quicksort example

@@

>>>>

With two concrete examples from open-source projects we will try to
show the reader that compositionality is indeed useful in the analysis
of common code.

@@

A clean theoretical framework for compositional bounds sometimes
even allow to get better asymptotic bounds.  During our experiments
we found an example of this situation in some code from the cBench
benchmark suite.
%
\begin{lstlisting}
for (;;) {
    do { l++; tick(1); } while (l < h && nondet());
    do { h--; tick(1); } while (h > l && nondet());
    if (h <= l) break;
    tick(1); /* swap two elements */ }
\end{lstlisting}
%
The above snippet is the inner loop of a Quicksort implementation, more
precisely, it is the partitioning part of the algorithm.  This partition
loop has linear complexity, and feeding into our analysis gives the
correct and tight worst-case bound $2+3|[l,h]|$.  However, all available
tools for C will derive a quadratic bound instead.  With the amortized
analysis approach in mind, it is clear that the three loops get their
potential from the same interval $[l,h]$.  But on the other hand, current
techniques will try to find one linear ranking-function for each loop
and combine them multiplicatively or additively, resulting in a loose
quadratic bound.
